Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-02 Report/decomposition_solutions.tex
Updated on 16.47:Jul-2

This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme. The formulation in \eqref{eqn-9} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered. In particular, the \ac{PD} and the \ac{ADMM} based \ac{DD} approaches are addressed.

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\set{\mc{B} \backslash \{b\}}} and \me{\bar{\mc{U}}_b} represents the set \me{\set{\mc{U} \backslash \mc{U}_b}}. The centralized problem defined by \eqref{eqn-9} can be equivalently written as
\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}
\underset{\substack{t_{l,k,n},\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
\end{IEEEeqnarray}
where \me{\tilde{\mbf{v}}_b} denote the vector of of weighted queue deviation corresponding to the users \me{k \in \mc{U}_b}.

Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized} and \cite{kaleva2013primal}, the interference constraint given by \eqref{eqn-9.1c} can be expressed by grouping the interference contribution from each \acp{BS} in the system as
\begin{IEEEeqnarray}{RCL}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \underbrace{\sum_{b \in \bar{\mc{B}}_{b_k}} \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}_{\text{neighboring \acp{BS} interference}} \; + \; N_0, \forall k \in \mc{U}.
\label{eqn-decent-2}
\end{IEEEeqnarray}
In \eqref{eqn-decent-2}, the neighboring \acp{BS} signals can be written explicitly using the relaxed expression as
\begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0, \IEEEyessubnumber \label{eqn-decent-3a}
\end{IEEEeqnarray}
where \me{\zeta_{l,k,n,b}}, which is the total interference caused by the \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
\begin{equation}
\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
\end{equation}

The expression in \eqref{eqn-decent-3} can be solved either by primal or by dual decomposition based on the usage of the coupling variable \me{\zeta_{l,k,n,b}} in the optimization problem. In both approaches, the distributed problem is solved by a two level optimization approach in which the local problems are solved at the \ac{BS} level and the master problem controls the variables involved in each local problem \cite{palomar2006tutorial}.

>>>>

This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme. The formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered. In particular, the \ac{PD} and the \ac{ADMM} based \ac{DD} approaches are addressed.

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}. The centralized problem\footnote{\eqref{eqn-9} for the \ac{SCA} approach and \eqref{eqn-mse-2} for \ac{MSE} reformulation approach} can be equivalently written as
\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}
\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
\end{IEEEeqnarray}
where \me{\tilde{\mbf{v}}_b} denote the vector of of weighted queue deviation corresponding to the users \me{k \in \mc{U}_b}.

Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint\footnote{coupling constraint in \ac{MSE} scheme is given by  \eqref{eqn-mse-2.3}} given by \eqref{eqn-9.1c} can be expressed by grouping the interference contribution from each \acp{BS} in the system as
\begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0, \label{eqn-decent-3a}
\end{IEEEeqnarray}
where \me{\zeta_{l,k,n,b}}, which is the total interference caused by the \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
\begin{equation}
\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
\end{equation}

The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the interference caused by the transmission from \ac{BS} \me{b} to the user \me{\ith{k}} corresponding data stream. In order the solve for the global optimal precoders, we need to find the optimal coupling variables \me{\zeta_{l,k,n,b}} by either using \ac{PD} or by using \ac{DD} method. In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} scheme and \eqref{eqn-mse-2.3} for the \ac{MSE} relaxation scheme are decoupled to perform the distributed precoder design problem.

### 2014-07-02 Report/mse_formulation.tex
Updated on 16.47:Jul-2

The \ac{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the set defined by the constraint \eqref{eqn-mse-1.2}. In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}. The first order Taylor approximation around a fixed \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}.
\label{mse-lin}
\end{IEEEeqnarray}

Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}. Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}. The optimization problem can be given as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
\end{IEEEeqnarray}

\subsubsection*{Convergence}
The convergence of the \ac{MSE} reformulation algorithm follows the similar comments drawn in \cite{christensen2008weighted,wmmse_shi}. Since at each \ac{KKT} point, the gradient of the original problem and the \ac{MSE} reformulation problem are made equal by the weights used in the \ac{MSE} reformulation, the problem is guaranteed to converge to the optimal solution by following the same stationary \ac{KKT} points.

>>>>

The \ac{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the constraint \eqref{eqn-mse-1.2}. In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}. The first order Taylor approximation around a fixed \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}.
\label{mse-lin}
\end{IEEEeqnarray}

Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}. Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}. The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
\end{IEEEeqnarray}

\subsubsection*{Convergence}
The convergence of the \ac{MSE} reformulation approach follows the same arguments detailed in \cite{wmmse_shi,christensen2008weighted}. Since the transmit precoders are obtained by minimizing the weighted \ac{MSE} criterion, it converges to the stationary \ac{KKT} point at each iteration. The receiver updates are made based on the \ac{MMSE} criterion, it provides the optimal receive beamformers for the given transmit precoders. Alternating between these two precoder designs guarantees the monotonicity of the objective function used in the problem \eqref{eqn-mse-2}. The \ac{MSE} relaxation method converges to the same stationary \ac{KKT} point as of the original \ac{WSRM} problem by making the graidents equal.

### 2014-07-02 Report/primal_approach.tex
Updated on 16.47:Jul-2

The centralized problem described in \eqref{eqn-decent-1} can be solved in a distributed approach using the \ac{PD} method. The decentralized approach decomposes the centralized problem as a two level optimization problem in which the multiple sub problems are coordinated using a master problem. The coordination of the multiple subproblems can be carried out by exchanging the information across the coordinating \acp{BS} in \me{\mc{B}} via backhaul. The distributed solution is achieved by fixing the interference level \me{\zeta_{l,k,n,b}, \forall k \in \mc{U}_{b_k}} from the \acp{BS} \me{b \in \bar{\mc{B}}_{b_k}} so as to decouple the variables \me{\zeta_{l,k,n,b}} \cite{pennanen2011decentralized,bertsekas1999nonlinear}. Now, the subproblems are governed by the master problem by updating the interference thresholds at each iteration using the subgradients.

As discussed in Section \ref{sec-4}, the constraint involving the coupling variables \eqref{eqn-9.1c} can be relaxed using the equivalent formulation in \eqref{eqn-decent-3}. Now, the subproblem for the \ac{BS} \me{b_k \in \mc{B}} can be obtained by grouping the terms relevant to the \ac{BS} \me{b_k} as
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-1}
\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
\text{subject to}&\quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_{b_k}} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \IEEEyessubnumber \label{eqn-primal-1c} \\
&& \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-primal-1d} \\
&& \zeta_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-primal-1e} \\
 & \quad & \text{and} \; \eqref{eqn-8} \IEEEyessubnumber,
\end{IEEEeqnarray}
where \me{\zeta_{\pr{l},\pr{k},n,{b_k}}} corresponds to the fixed maximum interference caused by the transmission from the \ac{BS} \me{b_k} to the \me{\ith{\pr{l}}} spatial stream of the \me{\ith{\pr{k}}} user. Let \me{\mbfa{\zeta}^{\set{b_k}}} be the vector representing the fixed interference levels relevant to the \ac{BS} \me{b_k} in a fully connected network (in practice it will be less), which is given by
\begin{IEEEeqnarray}{RCL} \label{eqn-primal-2}
\mbfa{\zeta}_{k,n,b} &=& \left [ \; \zeta_{1,k,n,b}, \dotsc, \zeta_{L,k,n,b} \; \right ] \IEEEyessubnumber \\
\mbfa{\zeta}^{\set{b_k}}_n &=& \left [ \; \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(1)}, \dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \right . \nonumber \\
&& \left . \dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(|\mc{U}_{b_k}|),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(1),n,b_k}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(|\bar{\mc{U}}_{b_k}|),n,b_k} \; \right  ] \IEEEyessubnumber \\
\mbfa{\zeta}^{\set{b_k}} &=& \left [ \; \mbfa{\zeta}^{(b_k)}_1, \dotsc, \mbfa{\zeta}^{(b_k)}_N \; \right ], \IEEEyessubnumber
\end{IEEEeqnarray}
where the length of the vector \me{\mbfa{\zeta}^{\set{b_k}}} is
\begin{equation}
n_{b_k} = | \mbfa{\zeta}^{\set{b_k}} | = \left ( |\bar{\mc{B}}_{b_k}| |\mc{U}_{b_k}| + |\bar{\mc{U}}_{b_k}|\right ) L N
\label{primal-vec-len}
\end{equation}

The problem defined in \eqref{eqn-primal-1} is already decoupled across the \acp{BS} by fixing the inter-cell interference vector \eqref{eqn-primal-2} for all \acp{BS}. For a fixed interference threshold \me{\mbfa{\zeta}^{\set{b}}}, the precoders are designed using \eqref{eqn-primal-1}. The local subproblem \eqref{eqn-primal-1} solved at each \ac{BS} are coordinated by the master problem, which updates the interference thresholds \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}} for the next iteration. The master and the subproblems follows the classical \ac{BCDM} approach to achieve the optimal solution by alternating the variable set while keeping other set constant in an iterative manner. The master problem controlling multiple subproblems is given by
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-3}
\underset{\mbfa{\zeta}}{\text{minimize}} & \quad & \sum_{b \in \mc{B}} \alpha^{\star}_b (\mbfa{\zeta}^{\set{b}}) \IEEEyessubnumber \\
\text{subject to} & \quad & \mbfa{\zeta}^{\set{b}} \in \mathbb{R}_+^{n_b}, \forall b \in \mc{B}, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\alpha^{\star}_b (\mbfa{\zeta}^{\set{b}})} denotes the optimal solution for \eqref{eqn-primal-1} with the previous value of \me{\mbfa{\zeta}^{(i-1)}}, where \me{\mbfa{\zeta}} is the global interference vector formed by stacking the interference vector associated with each \ac{BS} as \me{\mbfa{\zeta} = \left [ \mbfa{\zeta}^{\set{\mc{B}(0)}}, \mbfa{\zeta}^{\set{\mc{B}(1)}}, \ldots, \mbfa{\zeta}^{\set{\mc{B}(|\mc{B}|)}}\right ]}.

The master problem to find the optimal \me{\mbfa{\zeta}^{\set{b_k}(i)}, \forall b_k \in \mc{B}} is given by the following subgradient method \cite{bertsekas1999nonlinear} as
\begin{equation} \label{primal-sg-update}
\zeta^{\set{b_k}(i)}_{l,k,n,b} = \left [\zeta_{l,k,n,b}^{\set{b_k}(i-1)} - \rho \, s_{l,k,n,b}^{\set{b_k}(i-1)} \right ]^+, \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_b,
\end{equation}
where \me{i} is the iteration index, \me{\rho} is the positive step size, and \me{s^{\set{b_k}(i-1)}_{l,k,n,b}} is the subgradient of the problem defined in \eqref{eqn-primal-3} evaluated at \me{\zeta^{(i-1)}_{l,k,n,b}}. To find the subgradient \me{s^{\set{b_k}(i-1)}_{l,k,n,b}}, the dual variables corresponding to the interference constraints are required, which can be obtained by forming the Lagrangian of the primal problem \eqref{eqn-primal-2} as
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-4}
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \mu^{\set{b_k}}_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \nonumber + \left ( \beta_{l,k,n} - \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \right . \nonumber \\
&& \left . \quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{(i-1)}_{l,k,n,b} \; + \; N_0 \right ) \, \mu^{\set{b_k}}_{l,k,n}  \nonumber \\
&& + \quad \left ( \zeta^{(i-1)}_{\pr{l},\pr{k},n,{b_k}} - \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2 \right ) \, \mu^{\set{b_k}}_{\pr{l},\pr{k},n} , \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \\
\text{subject to} &\quad& \eqref{eqn-primal-1c} \; \text{and} \; \eqref{eqn-8} \IEEEyessubnumber.
\end{IEEEeqnarray}
Now the primal and the dual variables \me{\mu^{\set{b_k}}_{l,k,n}} and \me{\mu^{\set{b_k}}_{\pr{l},\pr{k},n}} corresponding to the constraints \eqref{eqn-primal-1d} and \eqref{eqn-primal-1e} are obtained by solving \eqref{eqn-primal-4}.

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}.

Once the interference vector converges \me{\mbfa{\zeta}^{\set{i}} \approx \mbfa{\zeta}^{\set{i-1}}} or iterated for certain times, say, \me{J_{\max}}, the \ac{SCA} update is performed by exchanging the transmit and the receive precoders to update the respective variables \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}}. The \ac{SCA} update can also be performed until convergence or for certain threshold \me{I_{\max}}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}. In this case, we perform \ac{SCA} and the receiver update at the same instant compared with the update of the recieve beamformers after the \ac{SCA} convergence. The approach followed in the algorithm provides the same solution as that of the separate update, since the receive beamformers are optimal for the given transmit precoders.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-4} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{\ac{PD} based decentralized \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

>>>>

The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}. Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3a}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration and is carried out until convergence. The primal approach is discussed extensively for the \ac{WSRM} problem in \cite{pennanen2011decentralized} and much of the current work follows the same. Much of the details are provided in the Appendix \ref{a-2}.

\subsubsection*{Convergence}
The convergence of the primal is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to the optimal values. But in practice, we can limit the number of exchanges to \me{J_{\max}} after which \ac{SCA} update is performed until convergence or for \me{I_{\max}} times. The update of \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} can be made in conjunction with the receiver update \me{\mvec{W}{k,n}}. The receiver update can be made by using the precoded pilot transmission from each user as in \cite{komulainen2013effective}.

### 2014-07-02 Report/problem_formulation_intro.tex
Updated on 16.47:Jul-2

The precoder design problem can be given minimizing the absolute value of the deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as \me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}. The exponent \me{q} plays a vital role in the final allocation, which will be discussed later. Now, the problem of weighted queued packet minimization formulated as a $q$-norm minimization, is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-3}
\underset{\substack{\mvec{m}{l,k,n},\\\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
\end{IEEEeqnarray}
where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, and \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission. It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users. In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels. Before discussing the formulation in detail, we first discuss the existing algorithm to solve the current issue of minimizing the number of backlogged packets at the transmitter.

>>>>

The precoder design problem can be given minimizing the absolute value of the deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as \me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}. The exponent \me{q} plays a vital role in the final allocation, which will be discussed later. Now, the problem of weighted queued packet minimization formulated as a $q$-norm minimization, is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-3}
\underset{\substack{\mvec{m}{l,k,n},\\\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
\end{IEEEeqnarray}
where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively. It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users. In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels. Before discussing the formulation in detail, we first discuss the existing algorithm to solve the current issue of minimizing the number of backlogged packets at the transmitter.
